### 2019-02-15 sections/intuition.tex
spelling

The central objective of \TOP is to \emph{coordinate collaboration}.
To this end, \TOPHAT has basic tasks called editors, whith which users can
interact, and combinators to express ways in which people can work together on
these tasks. Tasks can be executed after each other, at the same time, or
conditionally. This motivates the task combinators for steps, parallel
combination, and choice.
%One can say that tasks are a way to model \emph{workflows}.
% \TOPHAT is a language to specify workflows.

@@

Several oberservations can be made of a task. The most obvious and basic
observation is determining the value of a task. Not all tasks have a value
though, for example, the empty editor $\Enter \tau$ does not have a value.

>>>>

The central objective of \TOP is to \emph{coordinate collaboration}.
To this end, \TOPHAT has basic tasks called editors, with which users can
interact, and combinators to express ways in which people can work together on
these tasks. Tasks can be executed after each other, at the same time, or
conditionally. This motivates the task combinators for steps, parallel
combination, and choice.
%One can say that tasks are a way to model \emph{workflows}.
% \TOPHAT is a language to specify workflows.

@@

Several observations can be made of a task. The most obvious and basic
observation is determining the value of a task. Not all tasks have a value
though, for example, the empty editor $\Enter \tau$ does not have a value.
